---
title: "Airquality analysis"
author: "Johannes Damster"
date: "22nd of June 2021"
output: slidy_presentation
---

## Idea

This R Markdown presentation aims to analyse the linear relationship between airquality indicated by Ozone concentration and Temperature, Solar Radiation, and Wind. 

The output will be a scatterplot with a linear trend.

## Data

The dataset **airquality** allows to investigate the relationship between airquality (measured by Ozone concentration) and other meteorological variables like Temperature, Solar Radiation and Wind.

It comprises daily air quality measurements in New York, May to September 1973 and includes `r dim(airquality)[1]` observations on `r dim(airquality)[2]` variables.

```{r echo = FALSE, comment= ""}
head(airquality, n = 3)
```

Source: The data were obtained from the New York State Department of Conservation (ozone data) and the National Weather Service (meteorological data).

## Usage

This little programm plots a scatterplot of Ozone concentration over three different variables.
You can choose on the left which variable to use:

			- Temperature
			- Solar Radiation
			- Wind

It will also perform a linear regression resulting in a trendline.

## Example output

```{r echo = FALSE}
plot(airquality$Ozone~airquality$Solar.R, xlab = "Solar Radiation", ylab = "Ozone")
trend_Sol <- lm(airquality$Ozone~airquality$Solar.R, airquality)
abline(trend_Sol, col = "red")
```

## Important links

Please follow this link to use the App:
https://joda13.shinyapps.io/Temperature_analysis/

User Interface code:
https://github.com/Joda13/Dev_Data_Products/blob/main/ui.R

Server code:
https://github.com/Joda13/Dev_Data_Products/blob/main/server.R


Have fun!
               
